\documentclass[letterpaper]{article}
\author{Tim Visher\\ CMSCU 498\\ Chestnut Hill College}
\title{Cloud Computing and the Ideal Mobile Platform}

\usepackage{fullpage}
\usepackage{paralist}

\begin{document}

\Huge{

  \begin{center}
    \emph{Li-Ion}
  \end{center}}

\huge{

  Lithium-Ion battery technology was first proposed by M. S. Whittingham at
  Exxon in 1976.  Since then, advances have been made in their stability and
  capacity making them the preferred battery technology for many mobile
  applications.

  Lithium-Ion Batteries currently dominate the market of mobile power solutions
  for 2 main reasons:
  \begin{inparaenum}[(1)]
  \item Because of their physical structure, they are incredibly flexible in
    shape; and
  \item They do not suffer from issues of overcharging and charge memory that
    plagued traditional Nickel based rechargeable batteries.
  \end{inparaenum}

  Despite its obvious popularity, Lithium-Ion technology does have some
  disadvantages, namely:
  \begin{inparaenum}[(1)]
  \item A properly cared for Li-Ion battery will loose capacity at a strict and
    unavoidable rate, no matter what is done; and
  \item With the current physical structure of the electrodes today, battery
    capacity has plateaued.
  \end{inparaenum}

  The future of battery technology seems to lie in the direction of
  nano-technology research.  Nano-technologies greatly increase surface area
  over which the chemical reaction needed to produce power can take place
  yielding far higher capacitities.  This technology has only been successfully
  tested in laboratory environments.}

%% Say that tech hasn't been globally tested yet

\newpage

\Huge{

  \begin{center}
    \emph{Demand Management}
  \end{center}}

\huge{

  While battery technology has advanced at a steady pace since its inception,
  power needs of mobile devices has also increased at roughly the same rate
  yielding a net-gain of 0.  To get the best performance out of a mobile
  platform, one needs to practice demand management.

  Demand management is any practice that, when applied, reduces the load on the
  battery and thus allows the same battery to last longer between charges than
  if under heavier load.

  Many sources indicate that the following set of practices have the greatest
  effect on how much power a device is drawing.

  \begin{enumerate}

  \item Reduce the display brightness to the minimum workable level.

  \item Turn off any communication devices that aren't needed (WiFi, Bluetooth, etc.).

  \item Spin down the disks when they're not in use.

  \item Turn down the processor speed.

  \item Utilize Hibernate when the device is not in use.

  \end{enumerate}}

\end{document}
