My primary hypothesis is that mass adoption of ultra-mobile PCs will not happen
till customer hardware requirements are figured out.  Currently, the best
ultra-mobile PC battery life is 14 hours\footnote{Retrieved January 31, 2010
from\\ \url{http://www.netbookreviews.net/asus/eee-pc-1005pe-review/}}            %TODO
from the Eee PC 1005PE made by Netbook specialists ASUS.  That is not long        %Enter
enough to allow it to be on all day without charging.  Without hardware           %into
providing both the performance necessary to run today's cloud applications and    %bibliography
the inter-charge life expectancy to rival todays smart phones, Netbooks will
remain a niche product unless their price alone can be made compelling enough
that people accept the performance hit and begin to use them as their sole PC.

In close association with this hypothesis, the author intends to address the
following questions:

\begin{enumerate}

\item What about current mobile offerings is dissatisfying to the average
  consumer?  Despite enormous inroads into mobile PC sales made by Netbook
  manufacturers like ASUS and Acer, the primary drive for these PCs seems to be
  cost at this point\footnote{Where did this come from?}. %TODO Update
                                                               %reference

\item What would an ideal mobile offering for the average consumer look like?
  If it is indeed true that consumers still prefer traditional PCs over Netbooks
  and Smart-Phones, what would get people to switch to more of a mobile
  platform?  Would it be longer battery life?  Higher density screens?  Better
  software performance?  Would it matter if that performance was offered via
  that cloud or would it have to be local?

\end{enumerate}

Both of these questions are especially pertinent to the intended outcome of the
research project.  The author intends to create a paper prototype of a mobile
platform that is ideal to meet average consumer needs.

A second hypothesis is that Netbooks and traditional Notebook PCs are comparable
in the use of cloud services while they are unfavorably comparable in their
performance for traditional desktop usage.  In other words, when using a cloud
service, Notebooks and Netbooks will be just as performant, while doing the same
operations locally will produce a marked difference in performance.  This could
be proven by testing various cloud services and doing the same operations
locally.  A video could be encoded an a Notebook, a Netbook, and through both on
a service such as Vimeo or YouTube.  Time to completion could be
tested. Similarly, a large spreadsheet could be constructed on the 2 devices and
then on Google Docs, and performance could be compared.

The author's third hypothesis is that many people believe they use more of their
computer than they actually do.  At this point the author would have to measure
in some way what demands normal uses makes on a CPU and how that performance
differs between Netbooks and Notebooks.  The author could use the System
Requirements from a variety of popular software, for instance, to get general
benchmarks for what Systems are required to provide hardware-wise at this point.
The essential argument from many Netbook makers is that if you're primary use of
the computer is browsing the Web, writing and receiving e-mail, and preparing
documents and presentations in an office suite, then a Netbook will provide all
the computing performance you need.  The author would like to investigate the
validity of this point.

One question that the author would like to answer during this project is whether
considerations surrounding privacy affect peoples' opinion of cloud services at
this point or whether most people comfortable with a corporation housing and
protecting their private data.  The author imagines that most people who grew up
on the Internet would have a lack of a sense of privacy and so would not mind
giving that data away to be held by someone else that they have no direct
control over.  This would seem to be born out by the heavy use of services like
Facebook to store much of our private information.  The author would also expect
the answers to this question to be stratified across generations, with the older
generations being more likely to not trust a service with any of their data.

Almost certainly, the last 2 points will be impossible to get to in the time the
author has to complete the research.  They are, nonetheless, interesting thoughts. 
