\documentclass[12pt,oneside,letterpaper,titlepage]{report}
\author{Tim Visher\\ CMSCU 498\\ Chestnut Hill College}
\title{Cloud Computing and the Ideal Mobile Platform}

\usepackage[hyperindex=true,colorlinks=true]{hyperref}
\usepackage[all]{hypcap}
\usepackage{natbib}
\usepackage[version=3]{mhchem}
\usepackage[colorlinks=true]{hyperref}
\usepackage{paralist}
\usepackage{listings}
\usepackage{fullpage}
\usepackage{tabularx}

\lstset{basicstyle=\small}

\hypersetup{
    citecolor=blue,
    filecolor=blue,
    linkcolor=blue,
    urlcolor=blue
}

\begin{document}

\maketitle

\tableofcontents

\newpage

\begin{abstract}

Mobile platforms are currently designed to be less powerful but mobile versions
of desktop computers.  At the same time, extraordinary advances have been made
in the area of broadband Internet connectivity.  These advances have lead to the
explosion a software delivery strategy known as Cloud Computing; a resurgence of
the Client/Server computing model so prevalent in the early days of public
computing.  Cloud Services allow a computer to do many operations previously
only thought possible on a powerful local machine by sending the data and
instructions to a much more powerful third party computer and waiting to get the
results back.  The question the researcher is attempting to answer is:
Considering advances in Cloud Computing, what would the ideal mobile platform,
designed for longevity between charges and use of Cloud Services, look like?  In
order to answer this question, two areas of research were investigated: Battery
performance research was surveyed as the researcher believes that battery life is
one of the main culprits behind hampered mobile platform adoption, and
performance testing was done on a traditional Notebook PC and a Netbook PC to
ascertain whether the two devices' use of Cloud Services was identical or not.
The research proved that utilizing Cloud Services requires almost no local
processing power, except in the display of the results while at the same time
confirming that the performance differences between the two mobile platforms was
very noticeable when performing local operations.  The research also indicated
strongly that the main available area of improvement in the design of mobile
platforms is in demand management as research in battery technology especially
has stalled except for a few bright areas like that of utilizing nano technology
to build ultra-capacitive batteries.  The implications of this research lead the
researcher to conclude that the ideal mobile platform would enforce the use of
Cloud Services as a practice of demand management and focus almost all of it's
computational resources on efficiently displaying graphical data and maintaining
fast and reliable network connectivity.

\end{abstract}

\chapter{Introduction}

%% General Introduction

The purpose of this project is to discover the attributes of mobile computing
hardware specifically designed to take advantage of the current resurgence in
computing utilities collectively known as Cloud Computing.  The primary
motivation is that today's Netbook and ultra-mobile PC offerings are still being
designed within a desktop computing frame of mind where most of the work the
computer is going to do is to be taken care of locally.  It is believed that
there is a better design model for these computers in this new environment.  The
author's thesis is that there is a certain performance barrier beyond which
consumers will be willing to re-adopt the thin-client, time-sharing computer
model, that barrier being a combination of the usable life of the device between
charges and optimization for basic tasks performed locally as well as optimum
performance for services accessed via the Internet.  In order to discover this
hardware configuration, the usability of current Cloud Services and hardware
configurations will be investigated.

%% Cloud Computing

Amazon and other high-profile technology companies have already begun to offer a
wide variety of Cloud Services designed to place the brunt of the computational
and storage related burden on computers on the network rather than on the
customers' desktop machines \citep{reiss2008}.  These Cloud Computing services
are giving rise to a new class of applications, termed collectively by Tim
O'Reilly as Web 2.0, that focus on delivering effective software solutions via
the Internet rather than distributing them via shrink-wrapped packages
\citep{bleicher2006}.  Examples of such software included Google's office suite
Google Docs, their mail client GMail, YouTube's video encoding services,
Delicious's bookmarking and tagging services, and Abobe's web-based Photoshop
implementation.  What characterizes each of these services is two fold:
\begin{inparaenum}[(1)]
\item an emphasis on openness and collaboration; and
\item extremely low hardware requirements for the clients accessing them.
\end{inparaenum}
It is the low hardware requirements that are truly interesting for the research
being presented here.  These low requirements allow for a change in hardware
that could produce much longer run times without jeapordizing user experience.

Thus, the move to the Cloud Computing paradigm is happening and is just waiting
for someone to create a hardware platform that is truly optimized for that
environment.

%% Mobile Hardware

In tandem with and because of these developments in Cloud Computing, companies
such as ASUS are beginning to offer what have become known as netbooks or
ultra-mobile PCs.  These computers are stripped down versions of more
traditional notebook computers, in both power and size.  They are designed to
surf the web and do many of the other common things that computer users do
(e-mail, word processing, light gaming) while being very portable and
inexpensive.  Also, devices like the iPhone, Blackberry, and Palm, collectively
known as smart-phones, are revolutionizing the way people surf the web and think
about computing access.  GMail, Google's popular web based e-mail client, has a
version specifically designed to work with such small scale mobile computing
devices (as smart-phones are really much more than phones now) in deference to
the fact that many customers desire to be able to access the services they use
on the Web from anywhere at any time.  At the same time, efforts are being made
to give the experience of a desktop application to all mobile users, an effort
that is very hard to achieve on today's computing platforms (especially
smart-phones).

While these lower power machines are being developed today specifically because
the richness of the Web has put many people into their browser for most of their
day, today's mobile platforms are still being designed to be mobile desktop
computing environments.  This means that they are optimized for local operations
and sacrifice run time to remain performant.  The researcher believes this is
out of step with current trends in Cloud Computing.  Just like in the beginnings
of public computing, Cloud Computing centralizes on the idea of making software
available as a service accessed over cheap or rented hardware.  The problems
faced by the original software providers (public access to the Internet and the
cost of providing and procuring the hardware) are not faced by today's service
providers.  Broadband Internet connectivity is widespread at this point, at
least in the developed and increasingly so in the developing world and hardware
has dropped in price enough that most families are able to afford it.  Despite
these advances, mobile platform providers are still failing to capitalize on the
performance gains possible in the dependence upon Cloud Computing resources
which offload much of the processing power required to do computation to a
foreign machine and thus extend battery life greatly through demand management.
The design of such a device could change the way people of think of mobile
computing.

%% Question

The purpose of this research was to discover how the advent of Cloud Computing
will affect the design of mobile hardware.  Current mobile hardware is designed
with the idea of making a desktop computer mobile.  The emphasis is on local
computational power with applications and services that are hosted on your
machine.  The advent of Cloud Computing could allow for a redesign of mobile
platforms that focused on providing long battery life and high quality
connection to and use of Cloud Services rather than one that focuses on local
services that can also access the cloud as an aside.

The goal of the design would be to
\begin{inparaenum}[(1)]
\item Maximize battery life;
\item Maximize performance, perhaps through the design of a special processor
  that focuses on doing computation specific to utilizing web services
  efficiently; and
\item Minimize local computation to
  \begin{inparaenum}[(a)]
  \item displaying the UI;
  \item translating input; and
  \item maintaining network connectivity.
  \end{inparaenum}
\end{inparaenum}

%% Relevancy

The reason this research question is relevant is that Cloud Services are finally
beginning to gain real traction in the public's eye.  Many people are happy to
get their e-mail primarily through a web interface like GMail or Hotmail,
signaling a real change in public perceptions of performance, customizability,
and privacy.  Services like Google's Office Suite Google Docs, while still in
need of performance improvements, do perfectly serve for smaller spreadsheets,
documents, and presentations.  And they can be used on any platform with access
to a browser with exactly the same performance characteristics as on the most
performant machines today.  This reality allows for the design of a truly cloud
based mobile platform and reduces the barrier for entry for hardware owners to
extremely minimal machines with access to the Internet.

\chapter{Literature Review}

In light of the developments in Cloud Computing, this literature review will be
focused on a variety of topics all germane to the development of ultra-mobile
computers specifically designed for long, cell-phone like inter-charge life
expectancies and the use of Cloud Services.  One historical development that
needs to be covered is Time Sharing.  Time Sharing was a computing model born in
the days when computer hardware was very expensive.  The idea was that a
computer's computational time could be split between many users accessing the
machine over dumb terminals that did nothing but display output and send input.
The idea never really took off in the consumer sector, but it appears to be
making its comeback now.  In conjunction with this is the concept of a
thin-client, which despite the relative lack of a success of the time sharing
computing model has been very successful, especially in the medical space.
Thin-Client hardware is basically a dumb terminal optimized to display output
from a centralized server which may run any kind of operating system.  A great
deal of research has been done on the best way to implement thin-client
architectures, but the field is alive and well and very relevant to the
development of ultra-mobile PCs.

Rechargeable batteries play a significant role in almost every mobile electronic
device on the market today.  Often, battery life is the key component in the
consumers decision making process.  The iPhone was criticized harshly until a
firmware update enabled customers to get a day's worth of use out of it between
charges.  Google's G1 sank under similar criticisms.  Today's ultra-mobiles
don't offer battery life expectancy much greater than today's notebooks.  The
success of smart-phone technology over the ultra-mobile at the moment mainly
hinges on this distinction.

Cloud Computing, Web 2.0, and the developments concerning broadband Internet
access and Internet2 are also topics this literature review will be covering.
Cloud Computing is, as stated, a rehashing of the old time sharing model only
with much higher bandwidth and much broader access.  Web 2.0 is a loose
consortium of ideals that many of the companies providing their software as a
service adhere to \citep{oreilly2007}.  Broadband Internet is self explanatory.
These three technologies together provide the basis for why an ultra-mobile,
thin-client PC could be possible now when it could not have been 10 or 20 years
ago.  These technologies and the literature associated with them will be covered
in the following sections.

  \include{literatureReview}

\chapter{Research Project}

For the research portion of this project, two areas of investigation were explored:
\begin{inparaenum}[(1)]
\item Cloud Service performance using representatives of Netbook and Notebook
  hardware; and
\item Surveying battery performance research surrounding demand management as
  a way to extend battery life.
\end{inparaenum}
The research compiled can be found in \emph{section}~\ref{sec:batteryLiterature} on
\emph{page}~\pageref{sec:batteryLiterature}.  The performance research, on the other
hand, is original research and is outlined in detail in the following sections.

The performance testing consisted of utilizing Google Docs' Spreadsheet service
and OpenOffice.org to manipulate a test spreadsheet via a Notebook (MacBook) and
Netbook (asus ASPIRE one) computer.  Performance was observed via time to
complete operation measurements and CPU/Memory usages.

  \include{questionsAndHypotheses}

  \include{designMethodsAndProcedures}

  \include{discussion}

  \include{futureResearch}

\appendix

\chapter{Source Code}

This Appendix contains source code used in the process of completing the
research for this project.

\newpage

\label{sourceCode}
%\section{Source code from computer programs or other project}

\lstinputlisting[numbers=left,title=\lstname,frame=single,breaklines,label=randomSourceGen.groovy,caption=randomSourceGen.groovy]{randomSourceGen.groovy}

\newpage
\bibliographystyle{newapa}
\bibliography{bibliography}

\end{document}
